%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer - Development} % Job title
    {TrilaSoft Solution Private Limited} % Organization
    {Noida, Uttar Pradesh} % Location
    {Apr. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked as a Java Backed Developer and created new Web Application APIs for Customer Portal (Web Application that is build upon their legacy System (RedSky) that tracks the movement of goods from origin to destination) from the scratch.}
        \item {Successfully designed the APIs using latest technologies frameworks like Spring Boot, Hibernate, AWS Lambda, JPA, micro services etc}
        %\item {Implement the latest cloud technologies like AWS Lambda and AWS SAM(Serverless Application Model) CLI  for smooth and continuous deployments.}
        \item {Succored several go live production releases and propose operational feasibility and solution for the Web APP in AWS Cloud based architecture.}
        %\item {Continuously improved the infrastructure architecture since launching the service. (currently 10k users).}        
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Coforge Solutions (Erstwhile OnDemand Agility)} % Organization
    {Gurgaon, Haryana} % Location
    {Mar. 2021 - Apr. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
         \item {Worked on the platform migration architecture project as JAVA Big Data Engineer.}
        \item {Design the pipeline architecture to transformed the data of their legacy system to Hadoop Distributed File System using JAVA Big Data Frameworks like Apache Spark, Hadoop 2.0, impala SQL and Tectia SSH, etc.}
        \item {Performs Extract, Transform, Load aka ETL Operation so that the extracted data can be used for Business Intelligence Purpose.}
        \item {Regularly Developing the Big Data Attributes and their automation testing frameworks using Java Big Data tools and Cucumber Testing.}   
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer Trainee} % Job title
    {High Street Essential Pvt. Ltd} % Organization
    {Noida, Uttar Pradesh} % Location
    {Feb.2020 - July. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked as an intern in the java Back-end Development team and explore the technologies like Spring Boot,Spring, Hibernate,micro services, etc.} 
        \item {Develop several REST APIs using Spring Boot Framework for their e-commerce websites.} 
      \end{cvitems}
    }

%---------------------------------------------------------
  
\end{cventries}
